# Timing
use `./mk1dWM_vardly.pl` and `./mk1dAttention.pl` +  `./getBestWorkingMemory.bash` and `./getBestAttentionTiming.bash` 

for WM, run deconvolves with `deconvolve/runAllDeconvovles.bash`
## Att 

## WM 
There are `n` trials to schedule in 360 seconds. Trials types (high/low load + same/different) occur equally. If catch trials are used, 1/3 of all are catch (1/2 before dly, 1/2 after dly). If varable delay is used on noCatch and "both". Delays are `1s` and `3s`, distributed evenly.

1. snd (cue )
1. isi
1. mem (load1 or load4)
1. [possible catch]
1. dly (short (1s) or long (3s) )
1. [possible catch]
1. RSP (response, aka probe: change and nochange)

1000 random schedules are created with exponentially sampled ITI and ISI with and without (1000 ea) variable delay, see `mk1dWM.pl` and `mk1dWM_vardly.pl`. The `1D` description of the schedule is fed to `3dDecovolve -nodata` and the `norm. std. dev.` extracted for contrasts of interest. See page 83 of [3dDeconvolve manual](http://afni.nimh.nih.gov/pub/dist/doc/manual/3dDeconvolve.pdf): lower std is more power, **want small values**.

|          |both|noCatch|short|noCatchShort|
|----      |----|-------|-----|------------|
|ITI       |2.5 | 2     |7.5  |2.5         |
|fullTrials| 36 |48     |36   |48          |
|trials    | 48 |48     |48   |48          |

TODO: show collinearity
```{r constants}
## Power = Pr(Z>x)  where Z ~ N(0,1)

k=3   # alpha=.0013
s=15  # mesure error std dev
AB=10 # a>b by 10 IRF of A 10 units greater than B
AB=-10  # a<b by 10 
# error function (normal cdf) 
erf <- function(x) 2 * pnorm(x * sqrt(2)) - 1
# Pr(Z>x)
prz <- function(x) 1-1/2*(1+erf(x/sqrt(2)))
# page 87 afni 3dDeconvolve man, x is the norm std dev
afniprz <- function(x) prz( k- (AB/(s*x))  )
```

```{r setup,echo=F}
# render file with
#library('knitr')
#knit('timingInfo.Rmd')
##knitr::opts_chunk$echo=F
# prepare data
library(plyr)
library(ggplot2)

sofile  <- Sys.glob('deconvolve/shortDelay.out/*.stds.txt')
slfile  <- Sys.glob('deconvolve/vardly.out/*.stds.txt')
ncfile  <- Sys.glob('deconvolve/noCatch.out/*.stds.txt')
ncsfile <- Sys.glob('deconvolve/noCatchShort.out/*.stds.txt')
so <- adply(sofile, 1,function(x){read.table(header=F,x,sep="\t")})[,2:5]
sl <- adply(slfile, 1,function(x){read.table(header=F,x,sep="\t")})[,2:5]
nc <- adply(ncfile, 1,function(x){read.table(header=F,x,sep="\t")})[,2:5]
ns <- adply(ncsfile,1,function(x){read.table(header=F,x,sep="\t")})[,2:5]
so$dly <- "short"
sl$dly <- "both"
nc$dly <- "noCatch"
ns$dly <- "noCatchShort"
stds <- rbind(rbind(rbind(so,sl),nc),ns);
names(stds)<-c('n','contrast','type','std','dly')
stds$contrast<-paste(stds$contrast,stds$type,sep=".");
stds$type <- NULL
stds$power <- afniprz(stds$std)
wide<-reshape(stds,direction="wide",idvar=c("n","dly"),timevar="contrast")
```

### Ranges
```{r ranges,echo=F}
stdranges<-ddply(wide, .(dly), function(d){
  sapply(grep('std.',names(wide)),function(x){range(d[,x])})
} )
names(stdranges)[2:length(names(stdranges))]<-names(wide)[grep('std.',names(wide))]
#print(stdranges)


g<-ggplot(stds,aes(x=dly,y=std,color=dly))+theme_bw() +ggtitle('volin plot: dist. of std. dev. of est. of IRF/contrast')
p<-g + geom_violin() + facet_wrap(~contrast)
p<-g + geom_violin(aes(y=power)) + facet_wrap(~contrast)
print(p)
p<-ggplot(data=stds[grep('-.*LC$',stds$contrast),], aes(x=dly,y=power,color=dly)) + geom_point()  +geom_violin() + facet_wrap(~contrast) + theme_bw() + ggtitle('power')
print(p)
```


### Best
looking at event schedule with best mem-probe separation

```{r best,echo=F}
bestTable<-ddply(wide, .(dly), function(x){
  i<-which.min(x[,'std.mem-RSP']);
  data.frame(
     memVRSP=x[i,'std.mem-RSP'],
     bestMvR_mean=mean(unlist(x[i,grep('std.',names(x))]),na.rm=T ) 
  )
} )
print(bestTable)
```
